run_model_fitting

### 2019-01-08 bda/analysis/fit_model.Rmd
minor plot labeling

Compare to "optimal baseline" optimal in that `time` condition always pick short, `accuracy` always long, etc.
```{r}
bda_vs_baseline_plot <- df_predictives2 %>%
  mutate(baseline=ifelse(condition=='combined' & type=='frequent', 24,
                         ifelse(condition=='combined' & type=='infrequenty', 8,
                                ifelse(condition=='accuracy' & type=='frequent', 0,
                                       ifelse(condition=='accuracy' & type=='infrequent', 24,
                                              ifelse(condition=='time' & type=='frequent', 48, 16)))))) %>%
  gather('model', 'pred', c(baseline, estCnt)) %>%
  mutate(model=ifelse(model=='estCnt', 'BDA', 'Basline')) %>%
  ggplot(aes(x=actualCnt, y=pred, col=condition), alpha=0.4) +
    geom_point(aes(fill=condition), alpha=0.6, size=3, colour="white", pch=21) +
    geom_abline(intercept=0, slope=1, col='grey', alpha=0.4) +
    # geom_point(aes(x=actualInrequentProps, y=estInfrequentProps, col=condition), alpha=0.4) +
    facet_wrap(~model, scales="free") +
    ylab('Baseline model \n counts of short form') +
    xlab('Human data \n counts of short form') +
    theme_few()

>>>>

Compare to "optimal baseline" optimal in that `time` condition always pick short, `accuracy` always long, etc.
```{r}
bda_vs_baseline_plot <- df_predictives2 %>%
  mutate(baseline=ifelse(condition=='combined' & type=='frequent', 24,
                         ifelse(condition=='combined' & type=='infrequenty', 8,
                                ifelse(condition=='accuracy' & type=='frequent', 0,
                                       ifelse(condition=='accuracy' & type=='infrequent', 24,
                                              ifelse(condition=='time' & type=='frequent', 48, 16)))))) %>%
  gather('model', 'pred', c(baseline, estCnt)) %>%
  mutate(model=ifelse(model=='estCnt', 'BDA', 'Baseline')) %>%
  ggplot(aes(x=actualCnt, y=pred, col=condition), alpha=0.4) +
    geom_point(aes(fill=condition), alpha=0.6, size=3, colour="white", pch=21) +
    geom_abline(intercept=0, slope=1, col='grey', alpha=0.4) +
    # geom_point(aes(x=actualInrequentProps, y=estInfrequentProps, col=condition), alpha=0.4) +
    facet_wrap(~model, scales="free") +
    ylab('Baseline model \n counts of short form') +
    xlab('Human data \n counts of short form') +
    theme_few()
